High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-31 notebooks/intro.qmd
ufff

```{julia}
X = table(permutedims(counterfactual_data.X))
y =  counterfactual_data.output_encoder.labels
conf_model = conformal_model(clf; method=:simple_inductive)
mach = machine(conf_model, X, y)
fit!(mach)
```

@@

temp = 0.5
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, target=1, zoom=0, temp=temp, clim=nothing, loss_matrix=ones(2,2))
plot(p1, p2, size=(800,320))
```

@@

plts = []
for target ∈ counterfactual_data.y_levels
    sampler = CCE.EnergySampler(M, counterfactual_data, target; niter=niter, nsamples=100)
    Xgen = rand(sampler, nsamples)
    plt = plot(M, counterfactual_data; target=target, zoom=-3,cbar=false)
    scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
    push!(plts, plt)
end
plot(plts..., layout=(1,length(plts)), size=(img_height*length(plts),img_height))
```

@@

temp = 0.05
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=-1, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, zoom=-1, temp=temp, clim=nothing, loss_matrix=ones(4,4))
plot(p1, p2, size=(800,320))
```

>>>>

```{julia}
X = table(permutedims(counterfactual_data.X))
y =  counterfactual_data.output_encoder.labels
conf_model = conformal_model(clf; method=:trainable_simple_inductive)
mach = machine(conf_model, X, y)
fit!(mach)
```

@@

temp = 0.5
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, zoom=0, temp=temp, clim=nothing, loss_matrix=ones(2,2))
plot(p1, p2, size=(800,320))
```

@@

plts = []
for (i,target) ∈ enumerate(counterfactual_data.y_levels)
    sampler = CCE.EnergySampler(M, counterfactual_data, target; niter=niter, nsamples=100)
    Xgen = rand(sampler, nsamples)
    plt = plot(M, counterfactual_data; target=target, zoom=-3,cbar=false)
    scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=i,shape=:star,label="X|y=$target")
    push!(plts, plt)
end
plot(plts..., layout=(1,length(plts)), size=(img_height*length(plts),img_height))
```

@@

temp = 0.5
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=-1, temp=temp, clim=nothing)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, zoom=-1, temp=temp, clim=nothing, loss_matrix=ones(4,4))
plot(p1, p2, size=(800,320))
```
